D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-02-02 ootavacuous.tex
Add discussion of Hans Boehm's promote-to-acquire UB proposal
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

>>>>

\subsection{Atomic Stores From Undefined Behavior}
\label{sec:Atomic Stores From Undefined Behavior}

Another proposal to the C++ standards
committee~\cite{HansBoehm2020UBalternatives}
proposes (among other alternatives) that any atomic store resulting
from undefined behavior have at least release semantics.
This would prevent such a store from propagating undefined behavior
backwards within that store's thread.
In some cases, this could also prevent this undefined behavior from
propagating back through other threads.

However, it might well force C++ implementations to promote a surprisingly
large fraction of a program's relaxed stores to release.
